Interpretable Machine Learning

### 2018-06-04 talk-40min.Rmd
continues talk

---
title: "Interpretable Machine Learning"
author: "Christoph Molnar"
date: "December 4, 2017"
output: ioslides_presentation
css: styles.css
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
  warning = FALSE,
  message = FALSE, 
  fig.align='center')
```

@@

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("images/wow.jpg")
```

@@

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("images/magic.jpg")
```

@@

TODO: Insert image

@@

```{r, echo=FALSE, out.width='70%'}
knitr::include_graphics("images/done-here.gif")
```

@@

"There is a problem with the model!"

## What problem?

```{r, echo=FALSE}
knitr::include_graphics("images/Hide-the-pain-harold-phone.jpg")
```

## "The older the applicants, the higher the predicted salary, regardless of skills."
```{r, echo=FALSE, out.width='100%'}
knitr::include_graphics("images/age.jpeg")
```

@@

```{r}
pdp$results[pdp$results$.type == "pdp", c("Gender", ".y.hat")]
```

@@

- Opaque decision making by machine learning algorithms
- Examples: AI doctor, self-driving cars, creditworthiness
- Trust as a user: Should I start severe therapy, because the machine said so?
- Debugging as a practitioner: Why did the algorithm miss-classify sample X? Did it learn generalizable features?

![](images/black-box.png)

@@

Some things:
sparsity, contrastiveness, social, focus on the abnormal, truthful, coherent with prior beliefs, general and probable.

@@

(like, everything)

- Debugging
- Increasing trust

### Example: Doctor and ML

### Example: Predictive CV screening

- Nasty feedback loops
- Biased data
- Proxies instead of causality
-

## Example:

@@

![](images/black-box.png)

@@

![](images/white-box.png)

@@

![](images/black-box.png)

@@

![](images/specific-black-box.png)

@@

TODO: add images from papers
## Model-agnostic methods
![](images/black-box.png)

## Model-agnostic methods
![](images/agnostic-black-box.png)

@@

## Data-focused methods
![](images/black-box.png)

## Data-focused methods
![](images/data-box.png)

## Data-focused methods

>>>>

---
title: "Interpretable Machine Learning"
author: "Christoph Molnar"
date: "June 7, 2018"
output: 
  ioslides_presentation:
    widescreen: false
    smaller: false
css: styles.css
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
  warning = FALSE,
  message = FALSE, 
  fig.align='center', 
  out.width = '100%')
```

@@

```{r, echo=FALSE, out.height = '100%', out.width=NULL}
knitr::include_graphics("images/wow.jpg")
```

@@

```{r, echo=FALSE, out.height = '100%', out.width=NULL}
knitr::include_graphics("images/magic.jpg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("images/comp-dog.gif")
```

@@

```{r, echo=FALSE, out.height=NULL, out.width='100%'}
knitr::include_graphics("images/done-here.gif")
```

@@

Client: "There is a problem with the model!"

"What problem?""

```{r, echo=FALSE, out.height='50%'}
knitr::include_graphics("images/Hide-the-pain-harold-phone.jpg")
```

 Client: "Model predicts high salaries for old yet unskilled people."

```{r, echo=FALSE, out.height='30%'}
knitr::include_graphics("images/age.jpeg")
```

@@

@@

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("images/black-box.png")
```

- Opaque decision making by machine learning algorithms
- Bias and mistakes in the data
- Trust as a user: Should I start a therapy with sever side effects, because the machine said so?
- Debugging as a practitioner: Why did the algorithm miss-classify sample X? Did it learn generalizable features?

@@

Interpretability is also a mean to look at the data and possible issues with them.

@@

- Decisions about humans.
- Critical applications that decide about life and death.
- Newly developed systems with unknown consequences.
- Models using proxies instead of causal inputs.
- Debugging the models.
- Increasing trust.

### Examples where we need interpretability

- Credit scores
- Autonomous vehicles
- Medical recommendations
- Automated diagnoses

@@

```{r, echo = FALSE}
knitr::include_graphics("images/black-box.png")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("images/white-box.png")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("images/black-box.png")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("images/specific-black-box.png")
```

@@

TODO: add images from papers

```{r, echo=FALSE}
knitr::include_graphics("images/black-box.png")
```

```{r, echo=FALSE}
knitr::include_graphics("images/agnostic-black-box.png")
```

@@

## Example-focused methods

```{r, echo=FALSE}
knitr::include_graphics("images/black-box.png")
```

## Example-focused methods
```{r, echo=FALSE}
knitr::include_graphics("images/data-box.png")
```

## Example-focused methods
